Association between Breast Cancer and Hepatitis C Virus with Age Controlling

### 2022-12-06 manuscript/manuscript.tex
clean
added reference

\usepackage{amsmath}
\usepackage[margin = 1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage{array}

\usepackage{lipsum}
\usepackage[colorlinks=true, citecolor=blue]{hyperref}

@@

\begin{document}
\maketitle

@@

\begin{minipage}{\textwidth}
2x2 Contingency Table for all patients:

\begin{tabular}{ | m{4cm} | m{4cm}| m{4cm} | m{2cm} | }
  \hline
    & Breast Cancer & No Cancer Diagnosis & Total\\ 
  \hline
  HCV Seropositive & 88 & 15 & 103 \\ 
  \hline
  HCV Seronegative & 317 & 130 & 447 \\ 
  \hline
  Total & 405 & 145 & 550 \\ 
  \hline
\end{tabular}

@@

2x2 Contingency Table for pateints younger than 45:

\begin{tabular}{ | m{4cm} | m{4cm}| m{4cm} | m{2cm} | }
  \hline
    & Breast Cancer & No Cancer Diagnosis & Total\\ 
  \hline
  HCV Seropositive & 17 & 2 & 19 \\ 
  \hline
  HCV Seronegative & 110 & 91 & 201 \\ 
  \hline
  Total & 127 & 93 & 220 \\ 
  \hline
\end{tabular}

@@

2x2 Contingency Table for patients older than 45:

\begin{tabular}{ | m{4cm} | m{4cm}| m{4cm} | m{2cm} | }
  \hline
    & Breast Cancer & No Cancer Diagnosos & Total\\ 
  \hline
  HCV Seropositive & 71 & 13 & 84 \\ 
  \hline
  HCV Seronegative & 207 & 39 & 246 \\ 
  \hline
  Total & 278 & 52 & 330 \\ 
  \hline
\end{tabular}

@@

\end{minipage}

@@

\section{Discussion}
\label{sec:discuss}
  Based on the analysis, it is evident that for women under the age of 45,
seropositivity and breast cancer are strongly associated. As being HCV 
positive can complicate treatment of cancer, this is critical information.
In Egypt, breast cancer remains the most common form or cancer and high 
levels of hepatitus C continue. This study was retrospective so analysis 
was limited to observing odds ratios and the sample size was quite small.
Thus, future studies should aim to be prospective cohort studies so 
researchers can observe how seropisitivity and breast cancer interact 
over time. 
  Additionally, age is just one factor that can affect the associaiton 
between hepatitus C and breast cancer. Future studies should dive 
deeper into more factors such as weight, reproductive history, 
and alcohol consumption. Addiitonally, future studies can explore how 
seropositivity affects tumor size, disease agression, and more. As 
breast cancer is so prevalent in Egypt, further understanding the 
risk factors is becoming even more important.

\vspace{4cm}

>>>>

\usepackage{amsmath}
\usepackage[margin = 1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage{array}
\usepackage{caption}
\usepackage{setspace}
\usepackage[colorlinks=true, citecolor=blue]{hyperref}

@@

\doublespacing
\begin{document}
\maketitle

@@

\begin{center}
  \captionof{table}{2x2 Contingency Table for all patients}
\label{tab:all}
\begin{tabular}{rrrr}
  \toprule
  & Breast Cancer & No Cancer Diagnosis & Total\\ 
  \midrule
  HCV Seropositive & 88 & 15 & 103 \\ 
  HCV Seronegative & 317 & 130 & 447 \\ 
  \midrule
  Total & 405 & 145 & 550 \\ 
  \bottomrule
\end{tabular}
\end{center}

@@

\begin{center}
  \captionof{table}{2x2 Contingency Table for pateints younger than 45}
\label{tab:younger}
\begin{tabular}{rrrr}
  \toprule
  & Breast Cancer & No Cancer Diagnosos & Total\\
  \midrule
  HCV Seropositive & 17 & 2 & 19 \\ 
  HCV Seronegative & 110 & 91 & 201 \\ 
  \midrule
  Total & 127 & 93 & 220 \\ 
  \bottomrule
\end{tabular}
\end{center}

@@

\begin{center}
  \captionof{table}{2x2 Contingency Table for pateints older than 45}
\label{tab:older}
\begin{tabular}{rrrr}
  \toprule
  & Breast Cancer & No Cancer Diagnosos & Total\\
  \midrule
  HCV Seropositive & 71 & 13 & 84 \\ 
  HCV Seronegative & 207 & 39 & 246 \\
  \midrule 
  Total & 278 & 52 & 330 \\ 
  \bottomrule
\end{tabular}
\end{center}

@@

@@

\section{Discussion}
\label{sec:discuss}
  Based on the analysis, it is evident that for women under the age of 45,
seropositivity and breast cancer are strongly associated. As being HCV 
positive can complicate treatment of cancer, this is critical information.
In Egypt, breast cancer remains the most common form or cancer and high 
levels of hepatitus C continue. This study was retrospective so analysis 
was limited to observing odds ratios and the sample size was quite small.
Thus, future studies should aim to be prospective cohort studies so 
researchers can observe how seropisitivity and breast cancer interact 
over time.

Additionally, age is just one factor that can affect the associaiton 
between hepatitus C and breast cancer. Future studies should dive 
deeper into more factors such as weight, reproductive history, 
and alcohol consumption. Addiitonally, future studies can explore how 
seropositivity affects tumor size, disease agression, and more. As 
breast cancer is so prevalent in Egypt, further understanding the 
risk factors is becoming even more important.

\pagebreak
